Bioinformatics analysis of whole-genome bisulfite-sequencing data

### 2015-05-04 Rmarkdown/wgbs_bioinformatics_analysis.Rmd
Fix typesetting of --all-combinations

\begin{table}[h]
\centering
\begin{tabulary}{\textwidth}{LLLL}
\toprule
Software           & Reference                                & Input                                              & Limitations                                                                \\ \midrule
methclone & \citet{Li:2014ei}                       & \texttt{Bismark} \texttt{BAM}                                  & Unable to install \\
methpat  & \url{https://github.com/bjpop/methpat} & Output of \texttt{bme} & Designed for amplicons not whole-genome data.                                                                                 \\
DMEAS    & \citet{He:2013cj}                       & Output of \texttt{bme} & Windows operating system only. Perl code only available as PDF file.             \\
\bottomrule
\end{tabulary}
\caption[Software for calling methylation patterns at m-tuples]{Other software for methylation calling at m-tuples and their limitations. Abbreviations: \texttt{bme} =  \texttt{bismark\_methylation\_extractor}.}
\label{tab:other_m-tuple_methylation_callers}
\end{table}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/methtuple_example4.pdf}
\caption[\texttt{methtuple} 3-tuples with \texttt{--all-combinations}]{3-tuples produced for each read for the toy example in Figure \ref{fig:methtuple_example2} when the \texttt{--all-combinations} flag is set.}
\label{fig:methtuple_example4}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/methtuple_runtime.pdf}
\caption[\texttt{methtuple} running time]{The running times are the `User time' reported by \texttt{GNU time} converted from seconds to minutes. The suffix `ac' on the tuple size means that the option \texttt{--all-combinations} was set.}
\label{fig:methtuple_runtime}
\end{figure}

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/methtuple_memory.pdf}
\caption[\texttt{methtuple} memory usage]{The maximum memory usage is the `Maximum resident set size' reported by \texttt{GNU time} converted from kilobytes to gigabytes. These values are divided by four to fix bug in how \texttt{GNU time} reports the maximum memory usage (\url{https://bugzilla.redhat.com/show_bug.cgi?id=703865}). The suffix `ac' means that the option \texttt{--all-combinations} was set.}
\label{fig:methtuple_memory}
\end{figure}

>>>>

\begin{table}[h]
\centering
\caption[Software for calling methylation patterns at m-tuples]{Other software for methylation calling at m-tuples and their limitations. Abbreviations: \texttt{bme} =  \texttt{bismark\_methylation\_extractor}.}
\label{tab:other_m-tuple_methylation_callers}
\begin{tabulary}{\textwidth}{LLLL}
\toprule
Software           & Reference                                & Input                                              & Limitations                                                                \\ \midrule
methclone & \citet{Li:2014ei}                       & \texttt{Bismark} \texttt{BAM}                                  & Unable to install \\
methpat  & \url{https://github.com/bjpop/methpat} & Output of \texttt{bme} & Designed for amplicons not whole-genome data.                                                                                 \\
DMEAS    & \citet{He:2013cj}                       & Output of \texttt{bme} & Windows operating system only. Perl code only available as PDF file.             \\
\bottomrule
\end{tabulary}
\end{table}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/methtuple_example4.pdf}
\caption[\texttt{methtuple} 3-tuples with \texttt{{-}{-}all-combinations}]{3-tuples produced for each read for the toy example in Figure \ref{fig:methtuple_example2} when the \texttt{{-}{-}all-combinations} flag is set.}
\label{fig:methtuple_example4}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/methtuple_runtime.pdf}
\caption[\texttt{methtuple} running time]{The running times are the `User time' reported by \texttt{GNU time} converted from seconds to minutes. The suffix `ac' on the tuple size means that the option \texttt{{-}{-}all-combinations} was set.}
\label{fig:methtuple_runtime}
\end{figure}

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/methtuple_memory.pdf}
\caption[\texttt{methtuple} memory usage]{The maximum memory usage is the `Maximum resident set size' reported by \texttt{GNU time} converted from kilobytes to gigabytes. These values are divided by four to fix bug in how \texttt{GNU time} reports the maximum memory usage (\url{https://bugzilla.redhat.com/show_bug.cgi?id=703865}). The suffix `ac' means that the option \texttt{{-}{-}all-combinations} was set.}
\label{fig:methtuple_memory}
\end{figure}

\FloatBarrier
